Cross-validation of regression models: mixed model examples (edited v3)

### 2024-09-14 scratch/JSS-submission/Revision-1/Fox-Monette-cv-package.Rmd
modify intro to JSS paper

A number of existing \proglang{R} packages include functions for cross-validating regression models. We briefly situate the \pkg{cv} package relative to other \proglang{R} software for cross-validation in Section \ref{comparing-cv-to-other-r-software-for-cross-validation}.

@@

# Comparing cv to other R software for cross-validation

>>>>

A number of existing \proglang{R} packages include functions for cross-validating regression models. We briefly situate the \pkg{cv} package relative to other \proglang{R} software for cross-validation, and to other statistical software (in particular, \proglang{SAS}, \proglang{Stata}, and \proglang{Python}), in Section \ref{comparing-cv-to-other-software-for-cross-validation}.

@@

# Comparing cv to other software for cross-validation
